---
title: "tl:dr-Skript: Summary over the most important bits"
author: "Marcel Schliebs"
date: "2 Dezember 2017"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
library(haven)

knitr::opts_chunk$set(echo = TRUE)

gles <- read_spss(file = "C:/Users/Schliebs/OneDrive/github/ZU_teaching_applied_statistics/data/offline/gles/ZA6800_v1-0-0.sav",user_na = T)
```


This document shall recapitulate the most important bits we covered during the tutorial in Applied Statistics with R @Zeppelin University in Fall 17. If you have any questions, please shoot me an e-mail. Ich schreib das jetzt auf Englisch, da ich in Kontakt mit ein paar R-Teachern in Australien bin und ein wenig didaktische Methoden mit denen sharen will. Please forgive me.

# Indexing and Data Structure

We create a vector with electoral results
```{r,warning = FALSE}
x <- c(33,20.8,9,10,9,13)
```

And attribute party names to it
```{r,warning = FALSE}
names(x) <- c("CDU","SPD","GRUENE","FDP","LINKE","AFD")
```

Indexing by name
```{r,warning = FALSE}
x["AFD"]
```

Indexing by position
```{r,warning = FALSE}
x[2]
x[1] - x[2]
```

Select several elements
```{r,warning = FALSE}
jamaika <- x[c(1,3,4)]
sum(jamaika)
```

Indexing through logical vector
```{r,warning = FALSE}
sel <- c(TRUE,TRUE,FALSE,FALSE,FALSE,FALSE)
x[sel]
```


Calculate logical vector
```{r,warning = FALSE}
sel <- x > 20
```

And use for selection
```{r,warning = FALSE}
x[sel]
```

Overwrite elements
```{r,warning = FALSE}
x[1] <- x[1]-10
x[2] <- x[2]+10
x
```

FPD ? Not available any more...
```{r,warning = FALSE}
x[4] <- NA
x
```


# Loading Packages

Packages are collections of useful functions that fellow nerds wrote and put them online. One of the greatest benefits of R is its extremely rich framework of packages for every kind of use that you can imagine.

At first, we need to load some packages. If you do not have them installed them yet, please do so **once**. You can install a package by running the command `install.packages("NAME")` in R. 

The most important packages we got to know during the semester were:

Data management:
* `plyr`: Plyr is the older (and outdated) brother of tidyverse. We always need to load it once BEFORE (!) the latter in order to avoid nasty conflicts. 
* `tidyverse`: A very useful collection of tools for data-management. 
* `magrittr`: Gives us the beautiful Doppelpipe `%<>%`

Data Loading: 
* `haven` enables us to nicely import .sav or .dta Datasets.

Data Viz
* `ggplot2` is the most beautiful shit ever
* `ggthemes` and `hrbrthemes` make it even more brilliant
* `extrafont` fixes a problem with fonts for outputting plots to pdf

We load the most important packages
```{r,warning = FALSE}
library(plyr)
library(tidyverse)
library(magrittr)

library(haven)

library(ggplot2)
library(ggthemes)
library(hrbrthemes)
library(extrafont)
```


# Loading of the Dataset: 

Wir load the newest edition of the 2017-Bundestagswahl GLES study
```{r,warning = FALSE,eval=FALSE}

gles <- read_spss(file = "data/offline/gles/ZA6800_v1-0-0.sav",
                  user_na = T)

```

Ein erster Überblick
```{r,warning = FALSE}
str(gles)
head(gles)
```


# Daten Rekodieren

```{r,warning = FALSE}

```


# Einfache Scatterplots

## Zusammenhang Sympathie Jamaika ~ Migrationseinstellung

```{r,warning = FALSE}
                           
  
```



