---
title: "tl:dr-Skript: Summary over the most important bits"
author: "Marcel Schliebs"
date: "2 Dezember 2017"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("C:/Users/Schliebs/OneDrive/github/ZU_teaching_applied_statistics/R/load_datasets/01a_loaddata_gles.R")
```


This document shall recapitulate the most important bits we covered during the tutorial in Applied Statistics with R @Zeppelin University in Fall 17. If you have any questions, please shoot me an e-mail.  

# Loading Packages

Packages are collections of useful functions that fellow nerds wrote and put them online. One of the greatest benefits of R is its extremely rich framework of packages for every kind of use that you can imagine.

At first, we need to load some packages. If you do not have them installed them yet, please do so **once**. You can install a package by running the command `install.packages("NAME")` in R. 

The most important packages we got to know during the semester were:

Data management:
* `plyr`: Plyr is the older (and outdated) brother of tidyverse. We always need to load it once BEFORE (!) the latter in order to avoid nasty conflicts. 
* `tidyverse`: A very useful collection of tools for data-management. 
* `magrittr`: Gives us the beautiful Doppelpipe `%<>%`

Data Loading: 
* `haven` enables us to nicely import .sav or .dta Datasets.

Data Viz
* `ggplot2` is the most beautiful shit ever
* `ggthemes` and `hrbrthemes` make it even more brilliant
* `extrafont` fixes a problem with fonts for outputting plots to pdf


```{r,warning = FALSE}
library(plyr)
library(tidyverse)
library(magrittr)

library(haven)

library(ggplot2)
library(ggthemes)
library(hrbrthemes)
library(extrafont)
```


# Laden des Datensatzes: 


```{r,warning = FALSE,eval=FALSE}



```

Ein erster Überblick
```{r,warning = FALSE}
str(gles_data)

head(gles_data)

```

# Einfache Scatterplots

## Zusammenhang Sympathie Jamaika ~ Migrationseinstellung

```{r,warning = FALSE}
ggplot(data = gles_data,            # GGplot starten und Datensatz angeben
       aes(x = migration_z,        # Specify mapping: aestethics (variable stuff)
           y = jamaika_z))  + 
  geom_jitter()                              # jittered scatterplot
  
```

## Hinzufügen einer Regressionsgerade
```{r,warning = FALSE}
ggplot(data = gles_data,                          
       mapping = aes(x = migration_z,        
                     y = jamaika_z)) +  
  geom_jitter(color = "purple") + 
  geom_smooth(method = "lm") # lineare Regressionsgerade

```



## Unterscheiden nach Parteiidentifikation (farblich)

```{r,warning = FALSE}
ggplot(data = gles_data,                          
       mapping = aes(x = migration_z,        
                     y = jamaika_z,
                     col = pid)) +  # groupieren nach Color !
  geom_jitter() + 
  geom_smooth(method = "lm",se = FALSE) # wir schalten die Konfidenzintervalle aus 

```


## Die Farben sind hässlich: 
```{r,warning = FALSE}
ggplot(data = gles_data,                          
       mapping = aes(x = migration_z,        
                     y = jamaika_z,
                     col = pid)) +  
  geom_jitter(alpha = 0.4) +  # wir machen die Punkte ein bisschen durchsichtig
  geom_smooth(size = 2,method = "lm",se = FALSE)+ 
  scale_color_manual(values = c("afd" = "blue",  # wir weisen den Parteien farben zu
                                "fdp" = "yellow",
                                "gruene" = "green",
                                "keine" = "grey",
                                "linke" = "purple",
                                "spd" = "red",
                                "union" = "black"),
                     name = "PID",
                     labels = c("Die Blauen","Liberale","Ökos","Keine","Kommunisten","Sozis","Union"))
```


## Achsenlabels
```{r,warning = FALSE}
ggplot(data = gles_data,                          
       mapping = aes(x = migration_z,        
                     y = jamaika_z,
                     col = pid)) +  
  geom_jitter(alpha = 0.7) +  
  geom_smooth(size = 2,method = "lm",se = FALSE)+ 
  scale_color_manual(values = c("afd" = "blue",
                                "fdp" = "yellow",
                                "gruene" = "green",
                               "keine" = "grey",
                                "linke" = "purple",
                                "spd" = "red",
                                "union" = "black"),
                     name = "PID",
                     labels = c("AfD","FDP","Grüne","Keine","Linke","SPD","Union")) + 
  labs(x = "Migrationsfeindlichkeit", # Labels
       y = "Sympathie Jamaika",
       title = "Titel",
       subtitle = "Untertitel",
       caption = "Dieser Plot wird ihnen präsentiert von ZF")
```



## Schönes Theme
Jetzt noch ein Theme und sichern unter dem Objekt gg1
```{r,warning = FALSE}
gglala <-  # zuweisen
  ggplot(data = gles_data,                          
       mapping = aes(x = migration_z,        
                     y = jamaika_z,
                     col = pid)) +  
  geom_jitter(alpha = 0.7) +  
  geom_smooth(size = 2,method = "lm",se = FALSE)+ 
  scale_color_manual(values = c("afd" = "blue",
                                "fdp" = "yellow",
                                "gruene" = "green",
                                "keine" = "grey",
                                "linke" = "purple",
                                "spd" = "red",
                                "union" = "black"),
                     name = "PID",
                     labels = c("AfD","FDP","Grüne","Keine","Linke","SPD","Union")) + 
  labs(x = "Migrationsfeindlichkeit", 
       y = "Sympathie Jamaika",
       title = "Titel",
       subtitle = "Untertitel",
       caption = "whatever") + 
 theme_ipsum(grid = "Y") #Theme mit schöner Schrit und mit horizontalen Grid-Linien

gglala #print
```


## Output zum Einbinden ins Paper

### Entweder pdf
```{r,warning = FALSE,eval=FALSE}
ggsave(filename = "results/gles_jitterplot.pdf",
       plot = gglala,
       device = "pdf",
       width = 10,
       height = 6,
       dpi = 2000)
```


### oder png
```{r,warning = FALSE,eval=FALSE}
ggsave(filename = "results/gles_jitterplot.png",
       plot = gg1,
       device = "png",
       width = 10,
       height = 6,
       dpi = 2000)
```





#######################################################################

# Barplots Wahlentscheidung

## Eindimensional
```{r,warning = FALSE}
table(gles_data$zweitstimme)
```

## Häufigkeitsverteilung der Zweitstimme
```{r,warning = FALSE}
ggplot(data = gles_data) + 
  geom_bar(aes(x = zweitstimme))
```

               
## In Prozent
```{r,warning = FALSE}
ggplot(data = gles_data) + 
  geom_bar(aes(x = zweitstimme,
               y = (..count..)/sum(..count..), # relative häufigkeit 
               fill = zweitstimme))+ # Farblich
  scale_fill_manual(values = c("afd" = "blue",
                                "fdp" = "yellow",
                                "gruene" = "green",
                                "andere" = "grey",
                                "linke" = "purple",
                                "spd" = "red",
                                "union" = "black"),
                     name = "Zweitstimme",
                     labels = c("AfD","Andere","FDP","Grüne","Linke","SPD","Union"))
```


## Labels + Theme/Labels
```{r,warning = FALSE}
ggplot(data = gles_data,
       aes(x = zweitstimme,
           y = (..count..)/sum(..count..), # relative häufigkeit 
           fill = zweitstimme)) + 
  geom_bar(stat = "count")+ # Farblich 
  
  geom_text(aes(x = zweitstimme,
                y=..count../sum(..count..)+0.02,
                label=paste0(round(..count../sum(..count..)*100,1)," %"),
                color = zweitstimme), 
            stat="count")+
  scale_fill_manual(values = c("afd" = "blue",
                               "fdp" = "yellow",
                               "gruene" = "green",
                               "andere" = "grey",
                               "linke" = "purple",
                               "spd" = "red",
                               "union" = "black"),
                    name = "Zweitstimme",
                    labels = c("AfD","Andere","FDP","Grüne","Linke","SPD","Union"))+
  scale_color_manual(values = c("afd" = "blue",
                                "fdp" = "yellow",
                                "gruene" = "green",
                                "andere" = "grey",
                                "linke" = "purple",
                                "spd" = "red",
                                "union" = "black"),
                     name = "Zweitstimme",
                     labels = c("AfD","Andere","FDP","Grüne","Linke","SPD","Union"))+
  labs(x = "Partei", 
       y = "Anteil Zweitstimmen",
       title = "Titel",
       subtitle = "Untertitel",
       caption = "whatever") + 
  theme_ipsum(grid = "Y") #Theme mit schöner Schrit und mit horizontalen Grid-Linien
```




## Twodimensional Barplots  
```{r,warning = FALSE}

# Descriptive overview
round(
  prop.table(
  table(zweit = gles_data$zweitstimme,
        erst = gles_data$erststimme),margin = 1),2)


# In plot
gg1 <- #objekt zuweisen
  ggplot(data = gles_data,
         aes(x = zweitstimme,
             y = (..count..)/sum(..count..), 
             fill = erststimme)) + 
  geom_bar(stat = "count")+ 
  scale_fill_manual(values = c("afd" = "blue",
                               "fdp" = "yellow",
                               "gruene" = "green",
                               "andere" = "grey",
                               "linke" = "purple",
                               "spd" = "red",
                               "union" = "black"),
                    name = "Davon Erststimme",
                    labels = c("AfD","Andere","FDP","Grüne","Linke","SPD","Union"))+
  scale_color_manual(values = c("afd" = "blue",
                                "fdp" = "yellow",
                                "gruene" = "green",
                                "andere" = "grey",
                                "linke" = "purple",
                                "spd" = "red",
                                "union" = "black"),
                     name = "Davon Erststimme",
                     labels = c("AfD","Andere","FDP","Grüne","Linke","SPD","Union"))+
  labs(x = "Zweitstimme", 
       y = "Anteil Zweitstimmen",
       title = "Titel",
       subtitle = "Untertitel",
       caption = "whatever") + 
  theme_ipsum(grid = "Y")
gg1 #print
```



## Output to pdf
```{r,warning = FALSE,eval=FALSE}
ggsave(filename = "results/gles_barplot__stacked.pdf",
       plot = gg1,
       device = "pdf",
       width = 10,
       height = 6,
       dpi = 1000)
```


